An Analysis of Health & Lifestyle Factors Associated with Sleep Quality

### 2024-05-02 products/manuscript/Manuscript.qmd
check2

---
title: "An Analysis of Health & Lifestyle Factors Associated with Sleep Quality"
subtitle: ""
author: Kevin Kosewick and Emma Hardin-Parker
date: "4-29-2024"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: sleepref2.bib
csl: vancouver.csl
editor: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "An Analysis of Health & Lifestyle Factors Associated with Sleep Quality"
subtitle: ""
author: Kevin Kosewick and Emma Hardin-Parker
date: "4-29-2024"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/Sleep-MADA.bib
csl: ../../assets/apa.csl
editor: 
  markdown: 
    wrap: 72
---
